<!-- badges go here -->
[![Say Thanks!](https://img.shields.io/badge/Say%20Thanks-!-1EAEDB.svg)](https://saythanks.io/to/JohnCoene)
<!-- badges: end -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)

library(htmltools)
```

```{r, echo=FALSE}
br()
br()

div(
  class = "row",
  div(
    class = "col-md-4",
    img(
      src = "logo.png",
      class = "img-responsive responsive-img"
    )
  ),
  div(
    class = "col-md-8",
    p(
      "Text Analysis in R with Julia."
    ),
    p(
      tags$a(
        tags$i(class = "fa fa-rocket"),
        class = "btn btn-primary",
        href = "articles/get_started.html",
        style = "margin-bottom: 5px;",
        "Get Started"
      ),
      tags$a(
        tags$i(class = "fa fa-github"),
        class = "btn btn-default",
        href = "https://github.com/news-r/textanalysis",
        style = "margin-bottom: 5px;",
        target = "_blank",
        "Repository"
      )
    )
  )
)
```

## Installation

You can install the package with `remotes` from Github, see [changes](news/index.html).

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("news-r/textanalysis") # github
```

## Setup

The package's main dependency is [TextAnalysis.jl](https://github.com/JuliaText/TextAnalysis.jl) you therefore need a valid [Julia](https://julialang.org) installation on your machine.

You need to initialise every session with `init_textanalysis`, this will load the Julia dependencies and install them if required.

```r
textanalysis::init_textanalysis()
```

A few functions in the package depend on the _latest_ version of TextAnalysis which you can then isntall with.

```r
textanalysis::install_textanalysis("latest")
```
