---
title: "Latent Dirichlet Allocation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Latent Dirichlet Allocation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we attempt to fit a Latent Dirichlet Allocation model (LDA) to the reuters dataset. The dataset contains Reuters articles that fall on 10 different commodities: let's see if we can build a model to correctly classify those articles. 

> This is really to demonstrate how one would go about that. This example suffers from class imbalance, we do not split our dataset and simply train on the all documents.

```{r}
library(dplyr)
library(textanalysis)

init_textanalysis()

data("reuters")

count(reuters, category, sort = TRUE)

docs <- to_documents(reuters, text = text)
prepare(docs, strip_numbers = FALSE)
crps <- corpus(docs)

dtm <- document_term_matrix(crps)

lda_data <- lda(dtm, 10L, 10000L)

tfidf <- tf_idf(dtm)
km <- kmeans(tfidf, centers = 10L)

reuters %>% 
  mutate(class = km$cluster) %>% 
  count(class, category) %>% 
  arrange(class) %>% 
  filter(class == 3)
```
