---
title: "Naive Bayes Classifier"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Naive Bayes Classifier}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this example we use first names from NLTK to build a Naive Bayes classifier to predict gender. This is taken from the [NLTK book](https://www.nltk.org/book/ch06.html). This is a very basic example that only uses the last letter of the word to predict the gender but nonetheless achieves over 70% accuracy.

First we simply load the data and extract the last letter of each first name.

```{r}
library(dplyr)
library(textanalysis)

init_textanalysis()

classes <- factor(c("male", "female"))
model <- init_naive_classifer(classes)

# get data and shuffle
first_names <- nltk4r::first_names(to_r = TRUE) %>% 
  slice(sample(1:n())) %>% 
  mutate(last_letter = substr(name, nchar(name), nchar(name)))

head(first_names)
```

We can then split into training and testing data sets then initialise and train our model.

```{r}
# split
split <- floor(0.7 * nrow(first_names))
train <- first_names[1:split, ]
test <- first_names[(split + 1):nrow(first_names), ]

# train
train_naive_classifier(model, train, last_letter, gender)
```

Now we can predict and measure accuracy.

```{r}
# predict test
classes <- predict_class(model, test, last_letter)

# bind test and predictions
predicted <- test %>% 
  bind_cols(classes) %>% 
  mutate(
    predicted_gender = case_when(
      male > .5 ~ "male",
      TRUE ~ "female"
    ),
    accuracy = case_when(
      predicted_gender == gender ~ TRUE,
      TRUE ~ FALSE
    )
  )

# predictions
head(predicted)

# accuracy
sum(predicted$accuracy) / nrow(predicted)
```
