---
title: "Prepare"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Prepare}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(textanalysis)
init_textanalysis()
```

Text is inherently dirty and removes extensive cleaning, thankfully textanalysis has all the functions you need to obtain clean text ready to model. The core function to preprocess data is `prepare` as it always efficiently applying multiple `strip_*` functions.

- `prepare`
- `remove_case`
- `remove_corrupt_utf8`
- `remove_words`
- `strip_articles`
- `strip_indefinite_articles`
- `strip_definite_articles`
- `strip_preposition`
- `strip_pronouns`
- `strip_stopwords`
- `strip_numbers`
- `strip_non_letters`
- `strip_spares_terms`
- `strip_frequent_terms`
- `strip_html_tags`

The functions listed above apply to objects of class `document`, `documents`, and `corpus`, so we'll create a dirty document to clean.

```{r}
str <- "ThIs Is SoMe <span>vEry</span> Dirty TeXT!.!!"

(doc <- string_document(str))
```

Now we can apply the `prepare` function to the document.

```{r}
prepare(doc)
get_text(doc)
```

Notice something important, the document (`doc` object in our case) is cleanded _in place_. This means the function `prepare` does not return the cleaned input and rather cleans the object in the environment. This is useful when dealing with large amount of text as these _are not_ copied.

Though it may look like the document is now somewhat messed up with all the whitespaces inserted (as replacement to punctuation and other things) it is not, e.g.: textanalysis will still extract tokens correctly.

```{r}
get_tokens(doc)
```

Note that textanalysis also comes with a stemmer.

```{r}
stem_words(doc)
get_text(doc)
```

Also, though there are numerous functions to clean text all can be applied efficiently using `prepare`: the corresponsding Julia function applies them much more efficiently than using individually. You will likely not see a difference when working with a small number of documents. If you do use them separately ensure you apply them in the correct order, i.g.: do not strip the punctuation before the html tags (see example below).

```{r}
str <- "This is <span>html</span>."
doc <- string_document(str)

# DONT DO THAT
strip_punctuation(doc)
get_text(doc)
```
